Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-22 manuscript/manuscript.Rmd
new climate change figure

```{r figure_2, dependson="plot-options", fig.cap="Simulated changes species' median cover caused by a 1% increase in observed precipitation or temperature. We used the median of simulated results because the average was highly influence by some extreme outliers.", fig.width=4.5, fig.height=4, cache=FALSE, results='hide'}
# climBase <- readRDS("../montana/quadBM/simulations/climateChangeBase.rds")
# climPpt <- readRDS("../montana/quadBM/simulations/climateChangePrecip.rds")
# climTemp <- readRDS("../montana/quadBM/simulations/climateChangeTemperature.rds")
# climBoth <- readRDS("../montana/quadBM/simulations/climateChangePptTmp.rds")
# climBase$sim <- rep("Observed", nrow(climBase)) 
# climPpt$sim <- rep("Precipitation", nrow(climBase)) 
# climTemp$sim <- rep("Temperature", nrow(climBase)) 
# climBoth$sim <- rep("Both", nrow(climBase)) 
# climSimsQBM <- rbind(climBase, climPpt, climTemp, climBoth)
# # ggplot(climSimsQBM)+
# #   geom_boxplot(aes(x=species, y=cover*100, fill=sim))+
# #   scale_y_continuous(limits=c(0,10))
# climSimsQBMavg <- ddply(climSimsQBM, .(sim, species), summarise,
#                         avgCover = median(cover))
# climSimQBMcast <- dcast(climSimsQBMavg, formula = species~sim)
# climSimQBMcast$diffP <- with(climSimQBMcast, (Precipitation*100)-(Observed*100)) 
# climSimQBMcast$diffT <- with(climSimQBMcast, (Temperature*100)-(Observed*100))
# climSimQBMcast$diffB <- with(climSimQBMcast, (Both*100)-(Observed*100))
# climSimQBMplot <- melt(climSimQBMcast)
# climSimQBMplot <- subset(climSimQBMplot, species!="POSE")
# myCols2 <- c("#277BA8", "#7ABBBD", "#AED77A")
# ggplot(data=subset(climSimQBMplot, variable=="diffP"|variable=="diffT"|variable=="diffB"))+
#   geom_bar(aes(x=species, y=value, fill=variable), stat="identity", position="dodge", color="white")+
#   scale_fill_manual(name="", labels=c("1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=myCols2)+
#   theme_bw()+
#   theme(legend.position=c(0.6, 0.8))+
#   ylab("Cover Change (%)")+
#   xlab("Species")
```

>>>>

```{r figure_2, dependson="plot-options", fig.cap="Simulated changes species' median cover caused by a 1% increase in observed precipitation or temperature. We used the median of simulated results because the average was highly influence by some extreme outliers.", fig.width=4.5, fig.height=4, cache=FALSE, results='hide'}
climBase <- readRDS("../montana/quadBM/simulations/baselineSimulationQBM.rds")
climPpt <- readRDS("../montana/quadBM/simulations/pptChangeSimulationQBM.rds")
climTemp <- readRDS("../montana/quadBM/simulations/tempChangeSimulationQBM.rds")
climBoth <- readRDS("../montana/quadBM/simulations/temp-pptChangeSimulationQBM.rds")
climBase$sim <- rep("AObserved", nrow(climBase)) 
climPpt$sim <- rep("BPrecipitation", nrow(climBase)) 
climTemp$sim <- rep("CTemperature", nrow(climBase)) 
climBoth$sim <- rep("DBoth", nrow(climBase)) 
climSimsQBM <- rbind(climBase, climPpt, climTemp, climBoth)

myCols2 <- c("grey45", "#277BA8", "#7ABBBD", "#AED77A")
ggplot(climSimsQBM)+
  geom_boxplot(aes(x=species, y=cover*100, fill=sim), outlier.size=0)+
  theme_bw()+
  coord_cartesian(ylim=c(0,50))+
  scale_fill_manual(name="", labels=c("Observed", "1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=myCols2)

# climSimsQBMavg <- ddply(climSimsQBM, .(sim, species), summarise,
#                         avgCover = median(cover))
# climSimQBMcast <- dcast(climSimsQBMavg, formula = species~sim)
# climSimQBMcast$diffP <- with(climSimQBMcast, (Precipitation*100)-(Observed*100)) 
# climSimQBMcast$diffT <- with(climSimQBMcast, (Temperature*100)-(Observed*100))
# climSimQBMcast$diffB <- with(climSimQBMcast, (Both*100)-(Observed*100))
# climSimQBMplot <- melt(climSimQBMcast)
# climSimQBMplot <- subset(climSimQBMplot, species!="POSE")
# 
# ggplot(data=subset(climSimQBMplot, variable=="diffP"|variable=="diffT"|variable=="diffB"))+
#   geom_bar(aes(x=species, y=value, fill=variable), stat="identity", position="dodge", color="white")+
#   scale_fill_manual(name="", labels=c("1% Precipitation Increase", "1% Temperature Increase", "1% Temp. & Ppt. Increase"), values=myCols2)+
#   theme_bw()+
#   theme(legend.position=c(0.6, 0.8))+
#   ylab("Cover Change (%)")+
#   xlab("Species")
```
